Nitric-oxide-feedback to ciliary photoreceptor cells orchestrates UV avoidance

### 2022-08-19 text/Manuscript.Rmd
Add suplements

![**Figure 3. cPRC-specific expression of NIT-GC1 localises in close proximity to NOS in the ANS region.** (A) Phylogenetic tree of guanylate cyclase by maximum likelihood (ML). Guanylate cyclase-coupled receptor and soluble guanylate cyclase as outgroups. Guanylate cyclases with NIT domains are found in most animal phyla except Porifera, Ctenophora, Urochordata and Chordata. Tree robustness was tested with 1000 replicates of ultrafast bootstrap. Species names are as follows: Ap (Aiptasia pallida), Bb (Branchiostoma belcheri), Cv (Crassostrea virnigica), Dm (Drosophila melanogaster), Dp (Daphnia pulex), Hh (Hoilungia hongkongensis), Lg (Lottia gigantea), Pc (Priapulus caudatus), Pd (Platynereis dumerilii), Sk (Saccoglossus kowalevskii), Sp (Strongylocentrotus purpuratus), Ta (Trichoplax adhaerens), Tc (Tribolium castaneum). (B-D) Expression analysis of the NIT-GC1 gene (magenta) using in situ HCR. White arrowheads indicate cells expressing NIT-GC1. (B) Co-staining image using acetylated α-tubulin antibody (ac α-tub: green). (C) Co-expression analysis image of the c-opsin1 gene (green). Black arrowheads indicate cells expressing c-opsin1 differently from cPRC. (D) Co-expression analysis image of the MLD-pedal2 amide proneuropeptide gene (MLD-pNP: green). Black arrowheads indicate cells different from cPRC. The white dashed lines in (C) and (D) indicate the outer frame of the larvae. (E, F) Localisation analysis using NIT-GC1 and NIT-GC2 antibodies. Green shows co-staining with acetylated α-tubulin antibody (ac α-tub). (G) Co-localisation analysis using NIT-GC1 and NOS antibodies. (B-G) Anterior view of the 2-day-old larvae.](../figures/Fig3.png){width="100%"}

@@

![**Figure 4. NIT-GC1 is induced by NO to produce cGMP.** (A) Top: The domain structure of NIT-GC1. Grey squares indicate the transmembrane domain. Bottom shows a schematic of the NIT-GC1 assay; COS7 cells were used to express NIT-GC1 and the cGMP indicator Green cGull, and the NO donor SNAP and DMSO as control. Green cGull shows cGMP-dependent green fluorescence. (B) The intensity changes in cGMP fluorescence over time for the three conditions are shown. Gray traces show the optical responses to individual intensities (n = 6). The individual intensities are normalized (ΔF/F0). The dark line shows the mean value and the band the standard error range of the mean. The respective solution was acted on 2 min after the start of imaging (grey bars). (C) The mean intensity (Fmean/F0) after acting on the solution. Multiple comparisons were made using the Tukey honestly significant difference test.](../figures/Fig6.png){width="100%"}

>>>>

![**Figure 3. cPRC-specific expression of NIT-GC1 localises in close proximity to NOS in the ANS region.**  (A-D) Expression analysis of the NIT-GC1 gene (magenta) using in situ HCR. White arrowheads indicate cells expressing NIT-GC1. (B) Co-staining image using acetylated α-tubulin antibody (ac α-tub: green). (C) Co-expression analysis image of the c-opsin1 gene (green). Black arrowheads indicate cells expressing c-opsin1 differently from cPRC. (D) Co-expression analysis image of the MLD-pedal2 amide proneuropeptide gene (MLD-pNP: green). Black arrowheads indicate cells different from cPRC. The white dashed lines in (C) and (D) indicate the outer frame of the larvae. (E, F) Localisation analysis using NIT-GC1 and NIT-GC2 antibodies. Green shows co-staining with acetylated α-tubulin antibody (ac α-tub). (G) Co-localisation analysis using NIT-GC1 and NOS antibodies. (B-G) Anterior view of the 2-day-old larvae.NIT-GC1 is induced by NO to produce cGMP.** (A) Top: The domain structure of NIT-GC1. Grey squares indicate the transmembrane domain. Bottom shows a schematic of the NIT-GC1 assay; COS7 cells were used to express NIT-GC1 and the cGMP indicator Green cGull, and the NO donor SNAP and DMSO as control. Green cGull shows cGMP-dependent green fluorescence. (B) The intensity changes in cGMP fluorescence over time for the three conditions are shown. Gray traces show the optical responses to individual intensities (n = 6). The individual intensities are normalized (ΔF/F0). The dark line shows the mean value and the band the standard error range of the mean. The respective solution was acted on 2 min after the start of imaging (grey bars). (C) The mean intensity (Fmean/F0) after acting on the solution. Multiple comparisons were made using the Tukey honestly significant difference test.](../figures/Fig3.png){width="100%"}

@@
